---
title: "Week 3 Assignment"
author: "John Lin"
date: "6/20/2020"
output: ioslides_presentation
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(ggplot2)
library(plotly)
```

## Dataset

The `ToothGrowth` dataset contains information about the length of odontoblasts in 60 guinea pigs. Each animal received one of three dose levels of vitamin C (0.5, 1, or 2 mg/day) by one of two delivery methods, orange juice (OJ) or ascorbic acid (VC).

This presentation will show a scatterplot comparing the effects of dose and delivery method on tooth growth in guinea pigs.

## Code

```{r code, echo = TRUE}
levels(ToothGrowth$supp) <- c("Orange Juice", "Ascorbic Acid")
p <- ggplot(ToothGrowth, aes(x = factor(dose), y = len, color = supp)) + 
  geom_point() + 
  ggtitle("The Effect of Vitamin C on Tooth Growth in Guinea Pigs") + 
  xlab("Dose (mg/day)") +
  ylab("Tooth Length") + 
  scale_color_discrete(name = "Delivery Method")
p <- ggplotly(p)
```

## Plot

```{r plot, echo = FALSE}
p
```